An Invariant Framework for Conducting Reproducible Computational Science

### 2015-03-31 observation.tex
Stylistic
first paragraph

The application specifications of \emph{TauRoast} and \emph{Athena} were provided to us in the form of an
email that described in prose how to obtain the source,
build the program, and run it correctly on one specific
machine at our home institution, but with no particular guarantee that
it will run anywhere else in the world. This minimal level of documentation about software is routine in the scientific world. 
Below we describe the challenges faced when capturing the application details in a reproducible form and then preserving them for subsequent reuse:

>>>>

The application specifications of \emph{TauRoast} and \emph{Athena} were provided to us in the form of an
email that described in prose how to obtain the source,
build the program, and run it correctly on a specific
machine at our home institution.  There was no explicit guarantee that
it would run on other platforms. This minimal level of documentation about software is routine in the scientific world. 
Below we describe the challenges faced when capturing application details in reproducible form and then preserving them for subsequent reuse.
